---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Anna Teresa G. Aguilar"
date: "February 10, 2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation is submitted in partial fulfillment to the requirements for Developing Data Product Course offered by JHU

The Shiny application being pitched in this project can be accessed through : https://annaaguilar.shinyapps.io/CourseProject

The ui.R and server.R for the application can be accessed at: https://github.com/atgaguilar/Coursera-Developing-Data-Products



## Shiny App

The Shiny app process the 2017 Monthly Passenger Traffic per station of the Philippine National Railways (PNR)

The dataset is from Open Data Philippines (data.gov.ph)

In this application, average passenger traffic per month will be computed and will display a barplot of the passenger traffic for the month. 

## Example: 

Using dataset, Average passenger traffic for January may be computed and results will be as follow: 

```{r example, warning=FALSE}
library(plotly)

dataset<-read.csv("pnr_monthlypassengersperstation2017.csv", sep=",", header=T)

    average <-  mean(dataset[["January"]])
    plot_ly(data=dataset, x=dataset$Station, y=dataset$January,  type="bar") %>% 
      layout(title="Passenger Traffic" , xaxis=list(title="Station"), yaxis=list(title="Number of Passengers"))
```


# Thank you


